Modelling a Public Transport System in Real Time using a Particle Filter

### 2017-04-04 realtime-filter/realtime-filter.Rnw
add some text...

\documentclass[draft,a4paper,onecolumn]{IEEEtran}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

\title{Modelling a Public Transport System in Real Time using a Particle Filter}
\author{Tom~Elliott}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\section{Particle Filtering}
\label{sec:pf}

@@

Describe the data (GTFS static and real-time). (Maybe this go in section~\ref{sec:intro}?).

And the idea behind \emph{segmenting} bus routes between intersections.

>>>>

\documentclass{IEEEtran}
%\documentclass[draft,a4paper,onecolumn]{IEEEtran}

@@

\title{Modelling a Public Transport System in Real Time using a Particle Filter}
\author{Tom~Elliott}

\begin{document}

@@

@@

Our work makes use of publically available GTFS data,
which consists of the static component (timetables, shapes, etc),
and the real-time component (vehicle positions and stop time updates).
In its raw form, we are able to obtain the data,
model an individual bus, and determine its (unmeasurable) state
(see section~\ref{sec:transition}).

However, in order to model the network as a whole, 
we need to make some modifications to the data to enable us to 
separate vehicles from routes;
current methodologies, such as those by \ldots,
only use trips belonging to the same route.
In most networks, however,
there is a degree of overlap between routes,
and it is our intention to not only detect these overlaps,
but make full use of them.

We therefore need to be able to break routes into a series
of connecting segments, 
which can then be common between multiple different routes.
The simplest way to find all points at which any two routes 
may converge or diverge is at intersections.
Presently, we are using traffic light positions 
(easily obtained from OSM)
as an approximation for all intersections;
thus, there are some overlapping segments.
